Beyond Lip Reading - Inferring Voice Qualities from Visual Data

### 2024-04-08 PaperForReview.tex
Found additional papers that should be mentioned in "state of the art"

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

@@

@@

>>>>

%-------------------------------------------------------------------------
\subsection{Motivating Findings}

The finding that motivated our initial interest in this particular is our observations on the

@@

\subsection{Video to Audio Generation}

https://arxiv.org/abs/1910.10997 
Vision-Infused Deep Audio Inpainting

https://link.springer.com/chapter/10.1007/978-3-030-58621-8_44
Foley Music: Learning to Generate Music from Videos

@@

http://openaccess.thecvf.com/content_CVPR_2020/html/Prajwal_Learning_Individual_Speaking_Styles_for_Accurate_Lip_to_Speech_Synthesis_CVPR_2020_paper.html
Learning Individual Speaking Styles for Accurate Lip to Speech Synthesis

https://ieeexplore.ieee.org/abstract/document/10205038
ReVISE: Self-Supervised Speech Resynthesis with Visual Input for Universal and Generalized Speech Regeneration

#This one seems to be the latest w/ the highest quality - doesn't always get the speaker right but is pretty good
https://neha-sherin.github.io/RobustL2S/
https://ieeexplore.ieee.org/abstract/document/10317357
RobustL2S: Speaker-Specific Lip-to-Speech Synthesis exploiting Self-Supervised Representations
